% Last updated: 5/21/2017

\documentclass[11pt,letterpaper]{article}

\include{pkgs}
\input{cmds}

\begin{document}

% Name, phone, email, address
{\bf\huge Insu Yun} \vspace{1em}\\
\noindent\begin{tabular}[t]{@{}l}
  Room 3134, Klaus Advanced Computing Building \\
  Georgia Institute of Technology, \\
  266 Ferst Dr. N.W., Atlanta, GA, 30332-0765
\end{tabular}
\hfill
\begin{tabular}[t]{r@{}}
\\
Email: \email{insu@gatech.edu} \\
Web: \href{https://jakkdu.github.io}{https://jakkdu.github.io} \\
\end{tabular}

%
% Research Interests
%

\sectiontitle{Research Interests}
Binary analysis, system security and applied cryptography.

%
% Education
%

\sectiontitle{Education}
\begin{envtime}{Georgia Institute of Technology}{Aug. 2015 --}
	\item Ph.D. in Computer Science 
	\item Advisor: Dr. Taesoo Kim
\end{envtime}

\begin{envtime}{Korea Advanced Institute of Science and Technology (KAIST)}{Sep. 2008 -- Feb. 2015}
\item B.S. in Computer Science \& Mathematics
\end{envtime}

%
% Publications
%

\sectiontitle{Publications}
\begin{enumerate}
  \item \textbf{REPT: Reverse Debugging of Failures in Deployed Software} \\
  {\footnotesize
    Weidong Cui, Xinyang Ge, Baris Kasikci, Ben Niu, Upamanyu Sharma, Ruoyu Wang, and \textbf{Insu Yun} (alphabetical) \\
    In Proceedings of the 13th USENIX Symposium on Operating Systems Design and Implementation (OSDI 2018) \\
    Carlsbad, CA, October, 2018 \\
    \textbf{$\bullet$ Jay Lepreau Best Paper Award}
  }
  \item \textbf{QSYM: A Practical Concolic Execution Engine Tailored for Hybrid Fuzzing} \\
  {\footnotesize
    \textbf{Insu Yun}, Sangho Lee, Meng Xu, Yeongjin Jang, and Taesoo Kim \\
    In Proceedings of the 27th USENIX Security Symposium (Security 2018) \\
    Baltimore, MD, August, 2018 \\
    \textbf{$\bullet$ Distinguished Paper Award}
  }
  \item \textbf{AVPASS: Leaking and Bypassing Antivirus Detection Model Automatically} \\
  {\footnotesize
    Jinho Jung, Chanil Jeon, Max Wolotsky, \textbf{Insu Yun}, and Taesoo Kim \\
    BlackHat USA 2017 \\
    Las Vegas, NV, Auguest 2017
  }
  \item \textbf{CAB-Fuzz: Practical Concolic Testing Techniques for COTS Operating Systems} \\
  {\footnotesize
    Su Yong Kim, Sangho Lee, \textbf{Insu Yun}, Wen Xu, Byoungyoung Lee, Youngtae Yun, and Taesoo Kim \\
    In Proceedings of the 2017 USENIX Annual Technical Conference (ATC 2017) \\
    Santa Clara, CA, July 2017 
  }
  %
  \item \textbf{APISan: Sanitizing API Usages through Semantic Cross-checking} \\
  {\footnotesize
     \textbf{Insu Yun}, Changwoo Min, Xujie Si, Yeongjin Jang, Taesoo Kim, and Mayur Naik \\
     In Proceedings of the 25th USENIX Security Symposium (Security 2016), \\
     Austin, TX, August, 2016. \\
     \textbf{$\bullet$ Nominated as a finalist in CSAW Best Applied Research Paper Award 2016.}
  }
  %
  \item \textbf{HDFI: Hardware-Assisted Data-flow Isolation} \\
  {\footnotesize
    Chengyu Song, Hyungon Moon, Monjur Alam, \textbf{Insu Yun}, Byoungyoung Lee,
    Taesoo Kim, Wenke Lee, and Yunheung Paek. \\
    In Proceedings of the 37th IEEE Symposium on Security and Privacy (Oakland 2016), \\
    San Jose, CA, May, 2016.
  }
  %
  \item \textbf{Analyzing Security of Korean USIM-based PKI Certificate Service} \\
  {\footnotesize
    Shinjo Park, Suwan Park, \textbf{Insu Yun}, Dongkwan Kim, Yongdae Kim \\
    In Proceedings of the 15th International Workshop on Information Security Applications (WISA 2014), \\
    Jeju Island, Korea, Aug, 2014.
  }
  %
  \item \textbf{Kargus: a Highly-scalable Software-based Intrusion Detection System} \\
  {\footnotesize
    Muhammad Jamshed, Jihyung Lee, Sangwoo Moon, \textbf{Insu Yun}, Deokjin
    Kim, Sungryoul Lee, Yung Yi, and KyoungSoo Park. \\
    In Proceedings of The 19th ACM Conference on Computer and Communications Security (CCS 2012), \\
    Raleigh, NC, October, 2012.
  }
\end{enumerate}

%
% Work Experience
%

\sectiontitle{Work Experience}
\begin{envtime}[Research Intern, Seattle, WA]{Microsoft Research}{May. 2017 -- Aug. 2017}
\item Contributed to REPT, a system that utilizes Intel Processor Trace to diagnose production failures
  \item Mentor:  Weidong Cui
\end{envtime}
\subsectiontitle[Research Assistant, Atlanta, GA]{Georgia Tech}{Aug. 2015 --} \\
\begin{envtime}[Software Developer, Seoul, Korea]{Korean Cyber Command}{Apr. 2012 -- Jan. 2014}
  \item Served for the mandatory military service
\end{envtime}

% Honors & Awards
\sectiontitle{Honors \& Awards}
\begin{envtime}{Capture-the-flag(CTF) contests}{}
  \timeitem{DEFCON 26 CTF, 1st place (Team DEFKOR00T)}{Aug. 2018}
  \timeitem{DEFCON 24 CTF, 3rd place (Team DEFKOR)}{Aug. 2016}
  \timeitem{DARPA Cyber Grand Challenge (Team Disekt)}{Aug. 2016}
  \timeitem{Whitehat contest 2015 (Team SysSec)}{Nov. 2015}
  \timeitem{DEFCON 23 CTF, 1st place (Team DEFKOR)}{Aug. 2015}
  \timeitem{DEFCON 22 CTF, 10th place (Team GoN)}{Aug. 2014}
  \timeitem{SECCON CTF 2014, 1st place (TOEFL Beginner)}{Feb. 2014}
  \timeitem{Codegate CTF 2012, 3rd place (Team GoN)}{Apr. 2012}
  \timeitem{Secuinside CTF, 3rd place (Team GoN)}{Oct. 2011}
  \timeitem{ISEC CTF, 1st place (Team GoN)}{Sep. 2011}
  \timeitem{DEFCON 18 CTF, 3rd place (Team GoN)}{Aug. 2010}
  \timeitem{Codegate CTF 2010, 5th place (Team GoN)}{Apr. 2010}
  \timeitem{KISA HDCON, Gold Medal, 2nd place (Team GoN)}{May 2009}
  \timeitem{Codegate CTF 2009, 4th place (Team GoN)}{Apr. 2009}
\end{envtime}
%
\begin{envtime}{Bug Bounties}{}
  \timeitem{Three integer overflow vulnerabilities in PHP (\$1,500), the Internet Bug Bounty}{Jun. 2016}
  \timeitem{An Integer Overflow in Python zipimport (\$1,000), the Internet Bug Bounty}{Apr. 2016}
\end{envtime}
%
\begin{envtime}{Scholarships}{}
  \timeitem{National Research Foundation of Korea Scholarship for Undergraduate}{Mar. 2008 -- Dec. 2013}
\end{envtime}

% Teaching Experience
\sectiontitle{Teaching Experience}
\begin{envtime}{}{}
  \vspace{-0.5em}
  \timeitem{Teaching Assistant, Information Security Lab -- Official (CS8803 at Georgia Tech)}{Fall 2018}
  \begin{eval}
    \item Evaluation --  Overall Effectiveness: 5 / 5
  \end{eval}
  \timeitem{Teaching Assistant, Information Security Lab -- Unofficial (CS8803 at Georgia Tech)}{Fall 2017}
  \timeitem{Teaching Assistant, Information Security Lab -- Official (CS6265 at Georgia Tech)}{Fall 2016}
  \begin{eval}
    \item Evaluation --  Overall Effectiveness: 4.9 / 5
  \end{eval}
  \timeitem{Teaching Assistant, Information Security Lab -- Unofficial (CS6265 at Georgia Tech)}{Fall 2015}
  \timeitem{Head Instructor, Information Security class for freshmen (KAIST)}{Mar. 2009 -- Aug. 2011}
\end{envtime}

\end{document}
